---
title: "Lab 10: Interactive visualization"
author: "Lyrica Phelps"
date: "Date of lab session"
documentclass: article
geometry: margin=1in
fontsize: 11pt
output:
  html_document:
    highlight: tango
    self_contained: true
  pdf_document:
    highlight: tango
  github_document:
    html_preview: false
---

```{r setup, include = FALSE}
# DO NOT ALTER CODE IN THIS CHUNK
# Set knitr options
knitr::opts_chunk$set(
  echo = TRUE, eval = TRUE, fig.width = 5,
  fig.asp = 0.618, out.width = "80%", dpi = 120,
  fig.align = "center", cache = FALSE
)

# Load packages
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(highcharter))
suppressPackageStartupMessages(library(leaflet))

# Load dataset
mtcars <- read.csv("Cars.csv")
school <- read.csv("School_University_100.csv")

```
 
---

## Exercise 1

```{r}
hchart(mtcars, "scatter", hcaes(x = hp, y = mpg, group = cyl)) %>%
  hc_title(text = "Miles per gallon vs Gross horsepower") %>%
  hc_xAxis(title = list(text = "Gross horsepower")) %>%
  hc_yAxis(title = list(text = "Miles per gallon")) 
```

There is a general trend that as gross horsepower increases, the miles per gallon decrease. Also, in general the more cylinders there are, the lower the miles per gallon.

## Exercise 2

```{r}
hchart(mtcars, type = "bar", hcaes(x = Name, y = hp, group = carb)) %>%
  hc_title(text = "Gross horsepower and number of carburetors by car") %>%
  hc_xAxis(title = list(text = "Car")) %>%
  hc_yAxis(title = list(text = "Gross horsepower"))
```

```{r}
hchart(mtcars, type = "bar", hcaes(x = Name, y = hp, group = carb)) %>%
  hc_title(text = "Gross horsepower and number of carburetors by car") %>%
  hc_xAxis(title = list(text = "Car")) %>%
  hc_yAxis(title = list(text = "Gross horsepower")) %>%
  hc_add_theme(hc_theme_db()) 
```

NEED TO FIGURE OUT "Also, you can observe that there are 6 categories of the carburetor (1, 2, 3, 4, 6, 8). Please mention the name of the car(s) which have the highest gross horsepower in every category.""


## Exercise 3

```{r}
leaflet() %>%
  addProviderTiles(providers$Esri.DeLorme) %>%
  setView(lng = -98.4936, lat = 29.4241, zoom = 10)
```

The greater the number in used for "zoom", the more zoomed in the map is. There appears to be a limit, I saw no change between zoom = 200 and zoom = 400.

## Exercise 4

```{r}
leaflet() %>%
  addTiles() %>%
  setView(lng = -100.243683, lat =  34.052235, zoom = 3) %>%
  addCircleMarkers(lat = school$lat, lng = school$lon)
```

## Exercise 5

```{r}
leaflet() %>%
  addTiles() %>%
  setView(lng = -100.243683, lat =  34.052235, zoom = 3) %>%
  addMarkers(lat = school$lat, lng = school$lon,
             popup = paste("School name:", school$School_Name, "<br>",
                           "School rank:", school$School_Rank, "<br>",
                           "School URL:", school$School_Url)) 
```

